---
title: "Data Overview"
output: 
    html_notebook:
        theme: united
        highlight: tango
        toc: true
        toc_float: true
---

# Libraries
```{r}
library(tidyverse)
```


# Data

## Establish Relationships 

- Website traffic (Page Views, Sessions, Organic Traffic)
- Top 20 Pages

### Google Analytics - Summary Hourly

```{r}
# Google Analytics - Summary Hourly
read_rds("00_data/google_analytics_summary_hourly.rds")
```

- **Page Views**: Total Number of Pages viewed. Repeated views are counted. Spikes when promoted.
- **Organic Views**: Total Number of Pages viewed from people using unpaid search (i.e. Google search). Never spikes when promoted since this traffic is directed
- **Sessions**: A single session may have one or more pages viewed within a time frame. It can contain multiple page views but will only increment after a period of time has elapsed. Spikes when promoted.

### Google Analytics - Top 20 pages, Daily

```{r}
# Google Analytics - Top 20 pages, Daily
read_rds("00_data/google_analytics_by_page_daily.rds")
```

**`pagePath`**: Indicates the specific page that accumulated views. Can be from the domain (www.business-science.io) or one of the sub-domains (e.g. university.business-science.io). 

**`rank`**: Ranking based on the total Page Views. Gives us a rough idea of which pages get a lot of traffic, and therefore are most important to the business.

**Blog Articles**: Page Path contains `/category/date-of-publication/article-description`

**Course Landing Pages**: Page path contains `/p/course_desription`

## Build Relationships 

- Collect emails
- Host Events

### Mailchimp Data

```{r}
# Mailchimp Data
read_rds("00_data/mailchimp_users.rds")
```

**Database Exports**: Often you get data that is not a tidy time series. This one is at the user-level. It will need to be prepared before we can analyze it.

**Time-Based Aggregations**: We will typically summarise the data by an aggregation over time:

- Frequency(Counts)
- Sum
- Average

### Learning Labs

```{r}
# Learning Labs
read_rds("00_data/learning_labs.rds")
```

## Generate Course Revenue

- Revenue data (aggregated at weekly interval)
- Product Events

### Transactions Weekly

```{r}
# Transactions Weekly
read_rds("00_data/transactions_weekly.rds")
```

**Sales Revenue**: A key measure of performance that businesses need to forecast.

**Revenue Over Time**: Often the sales forecast is used in planning.

- How many people should we hire?
- Can we make an investment this quarter?

These questions are all based on a sales forecast.

**Revenue Aggregation**

Most databases don't have the revenue aggregated. Like the Mailchimp data, you will need to summarize the data by time.

### Product Events

```{r}
# Product Events
read_rds("00_data/product_events.rds")
```



